\documentclass{article}


\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=0.55in]{geometry}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{enumitem}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}
 
\usepackage{xcolor}

\renewcommand{\labelitemi}{$\textendash$}
\setlist{nosep}

\titleformat{\section}
{\Large\bfseries}
{}
{0em}
{}[\color{blue}\titlerule]

\titlespacing{\section}
{0em}{0.25em}{0.5em}

\titleformat{\subsection}[runin]
{\bfseries\large}
{}
{0em}
{}

\titlespacing{\subsection}
{0.75em}{0.25em}{0em}

\titleformat{\subsubsection}[runin]
{\bfseries}
{}
{0em}
{}[]

\titlespacing{\subsubsection}
{1em}{0.25em}{0em}

\titleformat{\paragraph}
{\normalfont\normalsize}
{}
{0em}
{}

\titlespacing{\paragraph}
{1em}{0.25em}{0em}



\renewcommand{\maketitle}{
\begin{center}
{\color{black}\huge\bfseries
\theauthor}

\vspace{.25em}
\href{mailto:cole@colekillian.com}{cole@colekillian.com} --- \href{https://colekillian.com}{colekillian.com} --- \href{https://github.com/ruborcalor}{github.com/ruborcalor} 
\end{center}
}


\begin{document}

\title{R\'esum\'e}
\author{Cole Killian}

\maketitle
\thispagestyle{empty} 

\section{Developer Skills\hfill\normalsize}

\subsubsection{Programming Languages} 
\hfill Javascript (React, Express), Python (Django, Locust), Bash, \LaTeX, Java, C++, Lua
\subsubsection{Tools/Services}
\hfill Google Cloud Platform, Google Cloud Computing, Firebase, Firestore, Stripe

\section{Experience}

\subsection{Harvard High Performance Computing: Web Dev and Performance Testing Intern \hfill 2020}
\begin{itemize}[leftmargin=0.5in]
  \setlength\itemsep{0.00em}
  \item Refactored the user account creation pipeline, increasing processing speed by \textbf{15} times (Python, Bash).
  \item Developed performance tests which exposed high load averages on web server hosts. Identified the source of the load and found a way to reduce it by \textbf{70\%} (Locust).
  \item Built a dashboard that enables non technical users to develop a thorough understanding of the Harvard super computer status (React, Passenger, Node).
    
\end{itemize}

\subsection{Artifai Co-Founder \hfill 2020}
\begin{itemize}[leftmargin=0.5in]
  \setlength\itemsep{0.00em}
\item Making \href{https://arxiv.org/abs/1508.06576}{neural style} technology available to non technical users, while streamlining the process for users to purchase their art on a poster/canvas.
\item Developed the backend for performing neural-style (Google Cloud Computing and Firebase Functions).
\item Developed the user authentication and social databases (Firebase, Firestore, and Node.js).
\item Built the user interface. Visit the business at \href{https://artif.ai}{https://artif.ai} (React, Webflow).
  % \item Poster/canvas production is made possible with \textbf{Printify} integration. Payments are handled with \textbf{Stripe}.
\end{itemize}

\subsection{NeuroTech: Dashboard Team \hfill 2020}
\begin{itemize}[leftmargin=0.5in]
  \setlength\itemsep{0.00em}
\item Worked with Neurotech to build a non-invasive forearm band that can predict which keys a user is typing without the need for a keyboard. Applications include augmented reality.
\item Developed a dashboard for visualizing realtime ML model predictions and signal data (React).
\item Built a server for interfacing between ML model predictions and frontend applications (SocketIO, Python).
\end{itemize}


\subsection{Age Prediction Via Methylation Data and Machine Learning \hfill 2019}
\begin{itemize}[leftmargin=0.5in]
  \setlength\itemsep{0.00em}
\item Developed a machine learning model for predicting a human's age based on the methylation data extracted from their blood sample (Keras).
\item Achieved \textbf{100\%} accuracy $\pm$10 years and $>90\%$ accuracy $\pm$5 years.
\item Developed a \href{https://epigenosys.com}{web interface} that enables clients to interact with the machine learning model. Users can tune each of the 25 features and see how predicted age changes (Django).
\item Presented research at McGill Science and Synergy. Made the front page of Hacker News with 112 upvotes.
\end{itemize}

\subsection{Libravos Co-Founder: Phone Insurance Made Better \hfill 2019-2020}
\begin{itemize}[leftmargin=0.5in]
  \setlength\itemsep{0.00em}
\item Accepted to McGill's Dobson Cup and Lean Startup Program. \href{https://docs.google.com/presentation/d/1mExXYPrHCWZ_4uRn0mu0f3_F_bhrw97eSgIJtMoN90k/edit?usp=sharing}{Pitchdeck}.
\item Developed an endpoint for a natural language processing ai chatbot. It communicated with a mobile phone app to help people learn about phone insurance (Rasa, React-Native). \href{https://devpost.com/software/libravos-mobile-app-with-chat-bot}{Devpost}
\end{itemize}

\subsection{Harvard High Performance Computing: Web Dev and Database Intern \hfill 2019}
\begin{itemize}[leftmargin=0.5in]
  \setlength\itemsep{0.00em}
  \item Developed a web interface that enables clients to view, request, or terminate their storage allocations (Django).
  \item Designed a mysql database model for tracking storage allocations and storage transactions (MySQL).
\end{itemize}

\subsection{Aspine Co-Founder: Website and PWA Development \hfill 2018 - 2019}
\begin{itemize}[leftmargin=0.5in]
  \setlength\itemsep{0.00em}
  \item Developed Aspine, an Open Source project that revolutionizes the user interface for Aspen, a grade checking service, with many new features and improved aesthetics (Node, HTML request mimicking). \href{https://github.com/Aspine/aspine}{Github} --- \href{https://aspine.us}{https://Aspine.us}
  \item Built an API for extracting student information from Aspen using HTML request mimicking (Node.js).
  \item Aspine is now preferred by over \textbf{500 students}.
\end{itemize}

% \subsection{FIRST Robotics Team Controls Co-Leader \hfill 2018 - 2019}
% \begin{itemize}[leftmargin=0.5in]
%   \setlength\itemsep{0.00em}
%   \item Developed a vision processing system for automating the operation of the robot using WPILib, a library desinged to simplify using OpenCV from a robot program.
%   \item Constructed a driver control system in Java that allowed the robot to be operated remotely over wifi via a joystick.
% \end{itemize}

% \subsection{Peer Partners: Admin, Developer, and Tutor \hfill 2016 - 2018}
% \begin{itemize}[leftmargin=0.5in]
%   \setlength\itemsep{0.00em}
%   \item Wrote a google scripts text mining program that saves the Peer Partners administration 100 hours a year by automating the parsing of a several thousand-row long google sheet
%   \item The script also aids with pairing those in want of academic assistance and those capable of delivering academic assistance.
%   % \item Designed a website to keep students up to date with their peer partners profiles
%   % \item Tutored high-school students in physics and math during lunch and after school.
% \end{itemize}

% \subsection{Plough and Stars (Restaurant): Social Media Manager \hfill 2018 - 2019}
% \begin{itemize}[leftmargin=0.5in]
%   \setlength\itemsep{0.00em}
%   \item Manage The Plough and Stars’s Instagram, Twitter, website, SEO, publicity, and performance recording.
%   \item Developed a python script using the Facebook Graph API that automatically uploads Facebook posts to Instagram.
% \end{itemize}

% \subsection{DC Sail: Sailing Instructor \hfill 2017 - 2018}
% \begin{itemize}[leftmargin=0.5in]
%   \setlength\itemsep{0.00em}
%   \item Led as a sailing instructor for the Kids Set Sail program.
%   \item Responsible for the education of six new students each week,  teaching them how to rig and de-rig a sailboat,  skipper and crew,  tie important knots, and work together effectively.
% \end{itemize}


% \hfill Intro to Software Systems, Intro to Computer Science, Abstract Algebra 1, Honors Analysis 1

% \subsubsection{Harvard University --- Concurrent Enrollment During High School --- CGPA 4.0}
% \hfill Multivariable Calculus, Linear Algebra and Differential Equations, Theoretical Physics

% \subsubsection{Cambridge Rindge and Latin HS (18-19)}
% \hfill AP Physics C: Mechanics (5), AP Physics C: Electricity and Magnetism (5)
% 
% \subsubsection{Bethesda-Chevy Chase HS (15-18)}
% \hfill AP Calculus BC (5), AP CS A (5), AP CS Principles (5), AP Statistics (5)

\section{Education\hfill\normalsize }

\subsubsection{McGill University --- B.Sc. Honors Stats and Comp Sci --- \href{https://colekillian.com/coursework-overview}{Coursework} --- CGPA 3.97 \hfill Expected 2022}


\section{Awards and Honors}

\paragraph{University: McGill Renewable Killam Entrance Scholarship, Faculty Of Science Scholarship}

\paragraph{High-school: Harvard Book Award, Straight A Award, Excellence in
  Mathematics Award, Outstanding French Award}


% \section{Extracurricular Activities}
% 
% \paragraph{Artificial Intelligence Club, Entrepreneur Club, Competitive Programming Club, Debate Team}
% \paragraph{Boston Sailing Center Frostbiting League. Placed first place out of twenty teams.}
% \paragraph{Competitive gymnast, Varsity diver, Varsity sailor, Captain of the winning Central Maryland Physics Olympics Team.}

\section{Hobbies and Interests}

\paragraph{Gym, playing guitar, walking, jogging, and hiking.}

\paragraph{Entrepreneurship, blogging, competitive programming, optimizing workflow (.spacemacs, .zshrc, .i3/config).}

% \paragraph{Optimizing my workflow (.spacemacs, .zshrc, .i3/config). Competitive programming.}


% \section{Technical Skills}
% 
% \subsubsection{Programming Technologies}
% \hfill GCP, Javascript (React, Node.js), Python (Django), \LaTeX, Java, C++, Bash

% \subsubsection{Operating Systems}
% \hfill Fluent: Linux/Unix environment --- Proficient: Windows XP/7/8/10, Mac OS

\end{document}




% Chess club
% Robotics club
% Diving