%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Harvard High Performance Computing} % Organization
    {Cambridge, MA} % Location
    {Jun. 2020 - September. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Refactored the user account creation pipeline, increasing processing speed by \textbf{15} times (Python, Bash). View \MYhref{https://ruborcalor.github.io/Academic-Cluster-Presentation/}{final presentation}.} 
      \item {Coded performance tests which exposed high load averages on web server hosts. Identified a way to reduce it by \textbf{70\%} (Locust).}
      \item {Built a dashboard that enables non technical users to understand the complex Harvard super computer status (React, Passenger, Node).}
        % \item {Implemented several API microservices in Node.js Koa and in the serverless AWS Lambda functions.}
        % \item {Deployed a centralized logging environment(ELK, Filebeat, CloudWatch, S3) which gather log data from docker containers and AWS resources.}
        % \item {Deployed a centralized monitoring environment(Grafana, InfluxDB, CollectD) which gather system metrics as well as docker run-time metrics.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-founder \& Software Engineer} % Job title
    {Artifai} % Organization
    {Cambridge, MA} % Location
    {Mar. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Making neural style technology available to non technical users, while streamlining the process for users to purchase their art on a poster/canvas.}
      \item {Architected the backend for performing neural-style (Google Cloud Computing and Firebase Functions).}
      \item {Developed the user authentication and social databases (Firebase, Firestore, and Node.js).}
      \item {Built the user interface. Visit the business at \MYhref{https://artif.ai}{https://artif.ai}. To date there have been over \textbf{300} users (React, Webflow).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {NeuroTech} % Organization
    {Montreal, QC} % Location
    {Feb. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Working with Neurotech to build a non-invasive forearm band that can predict which keys a user is typing without the need for a keyboard. Applications include augmented reality.}
      \item {Constructed a dashboard for visualizing realtime ML model predictions and signal data (React).}
      \item {Developed a pipeline for interfacing between ML model predictions and frontend applications (SocketIO, Python).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Fullstack Developer} % Job title
    {Epigenosys} % Organization
    {Montreal, QC} % Location
    {Sept. 2019 - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Engineered a machine learning model for predicting a human's age based on the methylation data extracted from their blood sample (Keras).}
      \item {Achieved \textbf{100\%} accuracy $\pm$10 years and $>90\%$ accuracy $\pm$5 years.}
      \item {Deployed a \MYhref{https://epigenosys.com}{web interface} that enables clients to interact with the machine learning model. Users can tune each of the 25 features and see how predicted age changes (Django).}
      \item {Presented research at McGill Science and Synergy. Made the front page of Hacker News with over \textbf{100} upvotes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Harvard High Performance Computing} % Organization
    {Cambridge, MA} % Location
    {May. 2019- August. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Deployed a web interface that enables \textbf{hundreds} of clients to view, request, or terminate their storage allocations (Django).}
      \item {Designed a mysql database model for tracking storage allocations and storage transactions (MySQL).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-founder \& Software Engineer} % Job title
    {Aspine} % Organization
    {Cambridge, MA} % Location
    {Jan. 2019, June. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Architected Aspine, an Open Source project that revolutionizes the user interface for Aspen, a grade checking service, with many new features and improved aesthetics (Node, HTML request mimicking). \MYhref{https://github.com/Aspine/aspine}{Github} --- \MYhref{https://aspine.us}{https://Aspine.us}. Aspine is now preferred by over \textbf{500 students}.}
      \item {Reverse engineered an API for extracting student information from Aspen using HTML request mimicking (Node.js).}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
